Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-07 paper/ijcai/paper.tex
new paper version, small changes

Aiming the evaluation of the \comb{} performance, three main 
experiements were performed: only using \sfl{} top calculate the statements
rank, . First, for each version

@@

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{llllll}
		\toprule
		Project             &  \# MFS-5  & \% MFS-5 & \# MFS-10 & \% MFS-10 & \# Faults \\ % & \#FS  & \# T & \# Ev & \#Bugs
		\midrule
		\chart{}  & 6 & 23.1\% & 4 & 15.4 \%  & 26\\ %& 40 &  57  &  136 & 21 
		% \closure{} 	& 3.7\% & 0\% & 96.3\%   \\ %& 56 &  10  &  81 & 6 
		% \lang{} 	& 0\% & 0\%  & 100\%   \\ % & 204 &  90  &  447 & 59 
		% \cmath{} 	& 2.1\% & 8\% & 89.9\%   \\ % & 299 &  112  &  438 & 86 
		% \mockito{} 	& 3.5\% & 3.3\% & 93.2\%   \\ % & 94 &  93  &  397 & 25 
		% \jtime{} 	& 0\% & 1.2\% & 98.8\%   \\ % & 63 &  49  &  171 & 16 
		\bottomrule
				%Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
	\end{tabular}
	\caption {Report of the capability of \ds{} on missing faulty statements}
\end{table*}
\normalsize

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[h]
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{llllllllllllll}
		\toprule
		   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
	red-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
	red-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
		   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
	red-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
	red-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
	\label{table:reduction}
\end{table*}

\begin{table*}[h]
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}p{1.75cm}p{0.8cm}p{1.6cm}p{1.3cm}p{0.8cm}p{1.2cm}p{0.8cm}p{0.8cm}p{0.8cm}p{1.5cm}p{1cm}p{0.8cm}p{1.3cm}p{0.8cm}@{}}
	\toprule
		   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
	SFL    & 36   & 265.5625    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
	\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
	\comb{}-10  & 35.5 & 406.375     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
	\cellcolor[HTML]{FFFFC7}IMP-5  & 20.5 & -450.9375   & 1.5         & 66  & 0.5         & 42  & 28 & 1.5  & 0            & 0.5    & 4  & -2390.5 & 9    \\
	\cellcolor[HTML]{FFFFC7}IMP-10 & 0.5  & -140.8125   & 1.5         & 59  & 0.5         & 42  & 26 & 1.5  & 0            & 0.5    & 4  & -2428.5 & 9    \\
	\cellcolor[HTML]{9AFF99}IMP    & {\success20.5} & X  & {\success1.5} & {\success66}  & {\success0.5} & {\success42}  & {\success28} & {\success1.5}  & 0 & {\success0.5} & {\success4}  & X & {\success9}    \\\midrule
		   & 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
	SFL    & 15.5 & 2471.1667 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.2143  & 6818.5 & 3  & 3516    & 140  \\
	\comb{}-5   & 15.5 & 2254.1667 & 9.1667 & 2   & 7.6667 & 2.5 & 6  & 21   & 105.4286  & 6818.5 & 3  & 6046.5  & 717  \\
	\comb{}-10  & 15.5 & 2264.8333 & 10.8333 & 2   & 7.6667 & 2.5 & 6  & 29.5 & 105.4286  & 6818.5 & 3  & 6063.5  & 140  \\
	\cellcolor[HTML]{FFFFC7}IMP-5  & 0    & 217         & 4.3333 & 0   & 1.8333 & 1   & 0  & 18   & -48.2143 & 0      & 0  & -2530.5 & -577 \\
	\cellcolor[HTML]{FFFFC7}IMP-10 & 0    & 206.3333 & 2.6667 & 0   & 1.8333 & 1   & 0  & 9.5  & -48.2143 & 0      & 0  & -2547.5 & 0    \\
	\cellcolor[HTML]{9AFF99}IMP    & 0    & {\success217} & {\success4.3333} & 0   & {\success1.8333} & {\success1}   & 0  & {\success18} & X & 0 & 0  & X & 0    \\ 
	\bottomrule
	\end{tabular}
	\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 (IMP-5) and top-10 (IMP-10) of the faulty classes}
	\label{table:performance}
\end{table*}
\normalsize

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	  \begin{tabular}{lrrr}
		\toprule
		Project            & \# (k = 5) & \# (k = 10) &  \% imp   \\ %\comments{& Failing Test Cases &}
		\midrule
		\lang{}            & 55 & 55 & 0 \%       \\   %\commentst{& 124   &  -}\\
		\cmath{}           & 87  & 91 & 3.77 \%     \\   %\comments{& 177   &  -}\\
		\closure{}         & 83  & 96  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 22  & 24 & 7.69 \%      \\  %\comments{& 92    &  -}\\
		\jtime{}           & 21  & 27 & 3.70 \%       \\   %\comments{& 76    &  -}\\
		\mockito{}         & 24  & 27 & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fs}
  \end{table}
  \normalsize

>>>>

Aiming the evaluation of the \comb{} performance, two different experiment

@@

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{llllll}
		\toprule
		Project             &  \# MFS-5  & \% MFS-5 & \# MFS-10 & \% MFS-10 & \# Faults \\ % & \#FS  & \# T & \# Ev & \#Bugs
		\midrule
		\chart{}  & 6 & 23.1\% & 4 & 15.4 \%  & 26\\ %& 40 &  57  &  136 & 21 
		% \closure{} 	& 3.7\% & 0\% & 96.3\%   \\ %& 56 &  10  &  81 & 6 
		% \lang{} 	& 0\% & 0\%  & 100\%   \\ % & 204 &  90  &  447 & 59 
		% \cmath{} 	& 2.1\% & 8\% & 89.9\%   \\ % & 299 &  112  &  438 & 86 
		% \mockito{} 	& 3.5\% & 3.3\% & 93.2\%   \\ % & 94 &  93  &  397 & 25 
		% \jtime{} 	& 0\% & 1.2\% & 98.8\%   \\ % & 63 &  49  &  171 & 16 
		\bottomrule
				%Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
	\end{tabular}
	\caption {\Sof{@todo: Improve caption} Report of the capability of \ds{} on missing faulty statements}
\end{table*}
\normalsize

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[h]
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{llllllllllllll}
		\toprule
		   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
	top-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
	top-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
		   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
	top-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
	top-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
	\label{table:reduction}
\end{table*}

\begin{table*}[h]
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}p{1.75cm}p{0.8cm}p{1.3cm}p{1cm}p{0.8cm}p{1cm}p{0.8cm}p{0.8cm}p{0.8cm}p{1cm}p{1cm}p{0.8cm}p{1.1cm}p{0.8cm}@{}}
	\toprule
		   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
	SFL    & 36   & 265.56    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
	\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
	\comb{}-10  & 35.5 & 406.38     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
	\cellcolor[HTML]{FFFFC7}$\Delta-5$  & 20.5 & -450.94   & 1.5         & 66  & 0.5         & 42  & 28 & 1.5  & 0            & 0.5    & 4  & -2390.5 & 9    \\
	\cellcolor[HTML]{FFFFC7}$\Delta-10$ & 0.5  & -140.81   & 1.5         & 59  & 0.5         & 42  & 26 & 1.5  & 0            & 0.5    & 4  & -2428.5 & 9    \\
	\cellcolor[HTML]{9AFF99}$\Delta$   & {\success20.5} & X  & {\success1.5} & {\success66}  & {\success0.5} & {\success42}  & {\success28} & {\success1.5}  & 0 & {\success0.5} & {\success4}  & X & {\success9}    \\\midrule
		   & 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
	SFL    & 15.5 & 2471.17 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.21  & 6818.5 & 3  & 3516    & 140  \\
	\comb{}-5   & 15.5 & 2254.17 & 9.17 & 2   & 7.67 & 2.5 & 6  & 21   & 105.43  & 6818.5 & 3  & 6046.5  & 717  \\
	\comb{}-10  & 15.5 & 2264.83 & 10.83 & 2   & 7.67 & 2.5 & 6  & 29.5 & 105.43  & 6818.5 & 3  & 6063.5  & 140  \\
	\cellcolor[HTML]{FFFFC7}$\Delta-5$  & 0    & 217         & 4.33 & 0   & 1.83 & 1   & 0  & 18   & -48.21 & 0      & 0  & -2530.5 & -577 \\
	\cellcolor[HTML]{FFFFC7}$\Delta-10$ & 0    & 206.33 & 2.67 & 0   & 1.83 & 1   & 0  & 9.5  & -48.21 & 0      & 0  & -2547.5 & 0    \\
	\cellcolor[HTML]{9AFF99}$\Delta$    & 0    & {\success217} & {\success4.33} & 0   & {\success1.83} & {\success1}   & 0  & {\success18} & X & 0 & 0  & X & 0    \\ 
	\bottomrule
	\end{tabular}
	\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 (IMP-5) and top-10 (IMP-10) of the faulty classes}
	\label{table:performance}
\end{table*}
\normalsize

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	  \begin{tabular}{lrrr}
		\toprule
		Project            & \# (k = 5) & \# (k = 10) &  \% $\Delta$   \\ %\comments{& Failing Test Cases &}
		\midrule
		\lang{}            & 55 & 55 & 0 \%       \\   %\commentst{& 124   &  -}\\
		\cmath{}           & 87  & 91 & 3.77 \%     \\   %\comments{& 177   &  -}\\
		\closure{}         & 83  & 96  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 22  & 24 & 7.69 \%      \\  %\comments{& 92    &  -}\\
		\jtime{}           & 21  & 27 & 3.70 \%       \\   %\comments{& 76    &  -}\\
		\mockito{}         & 24  & 27 & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fs}
  \end{table}
  \normalsize
